Linking hypothesis and number of response options modulate inferred scalar implicature rate

### 2018-10-31 manuscript.tex
minor edits to manuscript

@@

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  Are scalar inferences default inferences, in the sense that they arise
  unless blocked by (marked) contexts (Degen, 2015; Horn, 1984;
  Levinson, 2000)?
\item
  Are scalar inferences default inferences, in the sense that they are
  computed automatically in online processing and only cancelled by
  context in a second effortful step if required by context) (Bott \&
  Noveck, 2004; Breheny et al., 2006; Degen \& Tanenhaus, 2016; Grodner
  et al., 2010; Huang \& Snedeker, 2009; Politzer-Ahles \& Fiorentino,
  2013; Tomlinson et al., 2013)?
\item
  What are the (linguistic and extra-linguistic) factors that affect
  whether a scalar implicature is derived (Bergen \& Grodner, 2012;
  Bonnefon et al., 2009; Breheny et al., 2013, 2006; Chemla \& Spector,
  2011; De Neys \& Schaeken, 2007; Degen, 2015; Degen \& Goodman, 2014;
  Degen \& Tanenhaus, 2015, 2016; Marneffe \& Tonhauser, 2016; Potts,
  Lassiter, Levy, \& Frank, 2015; Zondervan, 2010)?
\item
  How much diversity is there across implicature types, and within
  scalar implicatures across scale types, in whether or not an
  implicature is computed (Doran, Ward, Larson, McNabb, \& Baker, 2012;
  Tiel et al., 2014)?
\item
  At what age do children acquire the ability to compute implicatures
  (Barner et al., 2011; Horowitz, Schneider, \& Frank, 2017; Katsos \&
  Bishop, 2011; Musolino, 2004; Noveck, 2001; Papafragou \& Tantalou,
  2004; Stiller, Goodman, \& Frank, 2015)?
\end{enumerate}

In addressing all of these questions, it has been crucial to obtain
estimates of \emph{implicature rates}. For 1., implicature rates from
experimental tasks can be taken to inform whether scalar implicatures
should be considered default inferences. For 2., processing measures on
responses that indicate implicatures can be compared to processing
measures on responses that indicate literal interpretations. For 3.,
contextual effects can be examined by comparing implicature rates across
contexts. For 4., implicature rates can be compared across scales (or
across implicature types). For 5., implicature rates can be compared
across age groups.

@@

Given the centrality of the theoretical notion of \enquote{implicature
rate} to much of experimental pragmatics, there is to date a surprising
lack of discussion of the basic assumption that it is adequately
captured by the proportion of ``FALSE' responses in truth value judgment
tasks (but see Benz and Gotzner (2014); Geurts and Pouscoulous (2009);
Degen and Goodman (2014); Katsos and Bishop (2011)). Indeed, the scalar
implicature acquisition literature was shaken up when Katsos and Bishop
(2011) showed that simply by introducing an additional response option,
children started looking much more pragmatic than had been previously
observed in a binary judgment paradigm. Katsos and Bishop (2011) allowed
children to distribute 1, 2, or 3 strawberries to a puppet depending on
\enquote{how good the puppet said it}. The result was that children gave
on average fewer strawberries to the puppet when he produced
underinformative utterances compared to when he produced literally true
and pragmatically felicitous utterances, suggesting that children do, in
fact, display pragmatic ability even at ages when they had previously
appeared not to.

@@

Consider a setup in which a listener is presented a card with a
depiction of either one or two animals (see Figure
\ref{fig:linkvisualization} for an example). As in a standard truth
value judgment task, the listener then observes an underinformative
utterance about this card (e.g., \enquote{There is a cat or a dog on the
card}) and is asked to provide a judgment on a scale with 2, 3, 4, or 5
response options, with endpoints \enquote{wrong} and
\enquote{right.}\footnote{An open question concerns the extent to which
  the labeling of points on the scale affects judgments (e.g.,
  \enquote{wrong}--\enquote{right} vs. \enquote{false}--\enquote{true}
  vs. \enquote{disagree}--\enquote{agree}). While some studies have used
  \enquote{false}--\enquote{true}, others have argued that judging truth
  may lead to meta-linguistic reasoning in participants that could
  distort judgments.} In the binary case, this reproduces the standard
truth value judgment task. Figure \ref{fig:linkvisualization}
exemplifies (some of) the researcher's options for grouping responses.
Under what we will call the \enquote{Strong link} assumption, only the
negative endpoint of the scale is interpreted as evidence for a scalar
implicature having been computed. Under the \enquote{Weak link}
assumption, in contrast, any response that does not correspond to the
positive endpoint of the scale is interpreted as evidence for a scalar
implicature having been computed. Intermediate grouping schemes are also
possible, but these are the ones we will consider here. Note that for
the binary case, the Weak and Strong link return the same categorization
scheme, but for any number of response options greater than 2, the Weak
and Strong link can in principle lead to differences in inferences about
implicature rate.

>>>>

\usepackage{color}
\definecolor{Blue}{RGB}{0,0,250}
\newcommand{\change}[1]{\textcolor{Blue}{[#1]}}

@@

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  Are scalar inferences default inferences, in the sense that they arise
  unless blocked by (marked) contexts (Degen, 2015; Horn, 1984;
  Levinson, 2000)?
\item
  Are scalar inferences default inferences, in the sense that they are
  computed automatically in online processing and only cancelled by
  context in a second effortful step if required by context (Bott \&
  Noveck, 2004; Breheny et al., 2006; Degen \& Tanenhaus, 2016; Grodner
  et al., 2010; Huang \& Snedeker, 2009; Politzer-Ahles \& Fiorentino,
  2013; Tomlinson et al., 2013)?
\item
  What are the (linguistic and extra-linguistic) factors that affect
  whether a scalar implicature is derived (Bergen \& Grodner, 2012;
  Bonnefon et al., 2009; Breheny et al., 2013, 2006; Chemla \& Spector,
  2011; De Neys \& Schaeken, 2007; Degen, 2015; Degen \& Goodman, 2014;
  Degen \& Tanenhaus, 2015, 2016; Marneffe \& Tonhauser, 2016; Potts,
  Lassiter, Levy, \& Frank, 2015; Zondervan, 2010)?
\item
  How much diversity is there across implicature types, and within
  scalar implicatures across scale types, in whether or not an
  implicature is computed (Doran, Ward, Larson, McNabb, \& Baker, 2012;
  Tiel et al., 2014)?
\item
  At what age do children acquire the ability to compute implicatures
  (Barner et al., 2011; Horowitz, Schneider, \& Frank, 2017; Katsos \&
  Bishop, 2011; Musolino, 2004; Noveck, 2001; Papafragou \& Tantalou,
  2004; Stiller, Goodman, \& Frank, 2015)?
\end{enumerate}

In addressing all of these questions, it has been \change{important} to obtain
estimates of \emph{implicature rates}. For 1., implicature rates from
experimental tasks can be taken to inform whether scalar implicatures
should be considered default inferences. For 2., processing measures on
responses that indicate implicatures can be compared to processing
measures on responses that indicate literal interpretations. For 3.,
contextual effects can be examined by comparing implicature rates across
contexts. For 4., implicature rates can be compared across scales (or
across implicature types). For 5., implicature rates can be compared
across age groups.

@@

Given the centrality of the theoretical notion of \enquote{implicature
rate} to much of experimental pragmatics, there is to date a surprising
lack of discussion of the basic assumption that it is adequately
captured by the proportion of ``FALSE' responses in truth value judgment
tasks (but see Benz and Gotzner (2014); Geurts and Pouscoulous (2009);
Degen and Goodman (2014); Katsos and Bishop (2011)). Indeed, the scalar
implicature acquisition literature was shaken up when Katsos and Bishop
(2011) showed that simply by introducing an additional response option,
children started looking much more pragmatic than had been previously
observed in a binary judgment paradigm. Katsos and Bishop (2011) allowed
children to distribute \change{a small, a big, or a huge strawberry } to a puppet depending on
\enquote{how good the puppet said it}. The result was that children gave
on average \change{smaller} strawberries to the puppet when he produced
underinformative utterances compared to when he produced literally true
and pragmatically felicitous utterances, suggesting that children do, in
fact, display pragmatic ability even at ages when they had previously
appeared not to.

@@

Consider a setup in which a listener is presented a card with a
depiction of either one or two animals (see Figure
\ref{fig:linkvisualization} for an example). As in a standard truth
value judgment task, the listener then observes an underinformative
utterance about this card (e.g., \enquote{There is a cat or a dog on the
card}) and is asked to provide a judgment on a scale with 2, 3, 4, or 5
response options, with endpoints \enquote{wrong} and
\enquote{right.}\footnote{An open question concerns the extent to which
  the labeling of points on the scale affects judgments (e.g.,
  \enquote{wrong}--\enquote{right} vs. \enquote{false}--\enquote{true}
  vs. \enquote{disagree}--\enquote{agree}). While some studies have used
  \enquote{false}--\enquote{true} \cite{bott2004, doran2012}, others have argued that judging truth
  may lead to meta-linguistic reasoning in participants that could
  distort judgments \change{\cite{XXX} XXX FIX}.} In the binary case, this reproduces the standard
truth value judgment task. Figure \ref{fig:linkvisualization}
exemplifies (some of) the researcher's options for grouping responses.
Under what we will call the \enquote{Strong link} assumption, only the
negative endpoint of the scale is interpreted as evidence for a scalar
implicature having been computed. Under the \enquote{Weak link}
assumption, in contrast, any response that does not correspond to the
positive endpoint of the scale is interpreted as evidence for a scalar
implicature having been computed. Intermediate grouping schemes are also
possible, but these are the ones we will consider here. Note that for
the binary case, the Weak and Strong link return the same categorization
scheme, but for any number of response options greater than 2, the Weak
and Strong link can in principle lead to differences in inferences about
implicature rate.
